### 2017-03-21 paper/paper.tex
Compiled and wrote about results

W
\hypersetup{
	colorlinks,
	citecolor=black,
	filecolor=black,
	linkcolor=black,
	urlcolor=black
}

\usepackage[backend=biber,style=authoryear]{biblatex}
\usepackage[newfloat]{minted}
\usepackage{csquotes}
\usepackage{caption}

@@

\usemintedstyle{vs}

@@

\begin{titlepage}
	\centering
	\vspace{2cm}
	{\Huge Analysis of voting systems: What should I call it? \par}
	\vspace{0.6cm}
	{\LARGE Adrian Salamon\par}

	\vspace{0.6cm}
	{\Large Kungsholmens gymnasium\par}
	\vspace{0.4cm}
	{\large Senior thesis\par}
	\vspace{0.6cm}
	\includegraphics[width=0.3\textwidth]{kg}\par\vspace{1cm}
	\vspace{4cm}
	\vfill
	Supervised by: \par
	Maja Kankaanranta

@@

\codeblock{code/typescriptexample.ts}{code:typescript example}{Basic Typescript syntax}

@@

In order to test the methods and their implementations, test data is needed. There are cases where extensive election data is published, such as in maltese elections, but full ballot data, which is needed for the implementations has not been found. Instead, the implementations will be tested with data generated from a simple computer algorithm. The algorithm used in this paper is highly primitive, as modeling prefrences within a population is far beyond this paper. The full ballot generation program can be found in the \Code{/generator/} folder. The goal of the program is to produce ballots that rank every candidate in order of prefrence (see figure \ref{STV ballot} on page \pageref{STV ballot}). The program represents each voter in a population as belonging to a certain ideology. Each ideology has has a list of weighted prefrences indicating how a voter for this ideology is likely to vote. The weighed prefrences are generated via an abstraction. A single config object is used to create all ideologies.
\codeblock{code/generator/ideologyConfig.ts}{code:ideology config}{Configuration object for creating ideologies}

@@

Scenario 1 is this:
\codeblock{code/generator/scenario1.ts}{code:scenario 1}{Scenario 1}

@@

\codeblock{code/fptp/inputs.ts}{code:fptp inputs}{Inputs for FPTP program}

@@

\codeblock{code/fptp/processing.ts}{code:fptp processing}{Processing and formatting of data}

@@

\codeblock{code/fptp/result.ts}{code:fptp result calculation}{Finding and returning winning candidates}

@@

	\label{STV ballot}

@@

\label{Stv psuedocode}

@@

The single transferable vote algorithm uses a tree structure to represent the state of the election. Every candidate is a top-level node with an attribute showing the number of current votes for the candidate. Each node has child nodes representing the next prefrences of the voters for that particular candidate, see figure \ref{Tree structure}. It is easy to manipulate branches via recursion. Merging and multiplying branches is used when transfering votes from one candidate node to another. A candidate node is a Typescript class. It can be found in the \Code{stv/candidate.ts} file and has the following properties and functions:

@@

	\label{Tree structure}

@@

\codeblock{code/stv/candidateNode.ts}{code:stv candidate node}{The CandidateNode class}

@@

\codeblock{code/stv/distribute.ts}{code:stv distribute function}{The distribute function}
In order to eliminate and transfer surplus votes from any candidate node $A$, the children of $A$ are passed into the distribute function. In the case of transfering surplus votes, the votes for each child node is first multiplied by $\frac{\text{surplus votes}}{\text{total votes}}$ as outlined in the psuedocode in section \ref{Stv psuedocode}. The full source code for funcions that manipulate the tree structure can be found in \Code{/stv/tree.ts}.

The main procces of the program is found in the \Code{stv/election.ts} file and runs the process defined in the psuedocode in section \ref{Stv psuedocode} on page \pageref{Stv psuedocode}.

\subsection{Schulze}
\subsubsection{Description}
The Schulze Method is a method used mainly to determine results in a single-winner election but can also be used to provide rankings and elect multiple candidates in a single election. Ballots are identical to those of the single transferable vote, see figure \ref{STV ballot} on page \pageref{STV ballot}. The method is compliant with the Condorcet Criterion, which means that if there is a candidate who the majority prefers in a pairwise comparison with every other candidate, that candidate wins. As mentioned, this method relies on comparing the prefrences of every candidate to one another as shown in table \ref{Pairwise comparison matrix}. If there is a condorcet winner the process is simple: declare the condorcet winner a winner and run another iteration without that candidate. Repeat this process until all seats are filled. However, there can be condorcet ties, where there is no condorcet winner. There are multiple ways of resolving the tie, one of them being the Schulze Method.

@@

The difficult problem in this method is finding the strongest path between candidates. The problem is called the widest path problem in graph theory. An efficent and relatively simple way to compute this problem is via the Floyd-Warshall algorithm which is used in the implementation. See \ref{Schulze psuedocode} for the full algorithm.

\begin{table}[H]
\centering
\begin{tabular}{l|c|c|c|c|c|}
\cline{2-6}
 & \multicolumn{1}{l|}{A} & \multicolumn{1}{l|}{B} & \multicolumn{1}{l|}{C} & \multicolumn{1}{l|}{D} & \multicolumn{1}{l|}{E} \\ \hline
\multicolumn{1}{|l|}{A} & \cellcolor[HTML]{9B9B9B} & \cellcolor[HTML]{FFDDDD}17 & \cellcolor[HTML]{FFDDDD}14 & \cellcolor[HTML]{DDFFDD}35 & \cellcolor[HTML]{DDFFDD}30 \\ \hline
\multicolumn{1}{|l|}{B} & \cellcolor[HTML]{DDFFDD}33 & \cellcolor[HTML]{9B9B9B} & \cellcolor[HTML]{FFDDDD}24 & \cellcolor[HTML]{DDFFDD}47 & \cellcolor[HTML]{DDFFDD}36 \\ \hline
\multicolumn{1}{|l|}{C} & \cellcolor[HTML]{DDFFDD}36 & \cellcolor[HTML]{DDFFDD}26 & \cellcolor[HTML]{9B9B9B} & \cellcolor[HTML]{DDFFDD}40 & \cellcolor[HTML]{DDFFDD}42 \\ \hline
\multicolumn{1}{|l|}{D} & \cellcolor[HTML]{FFDDDD}15 & \cellcolor[HTML]{FFDDDD}3 & \cellcolor[HTML]{FFDDDD}10 & \cellcolor[HTML]{9B9B9B} & \cellcolor[HTML]{FFDDDD}18 \\ \hline
\multicolumn{1}{|l|}{E} & \cellcolor[HTML]{FFDDDD}20 & \cellcolor[HTML]{FFDDDD}14 & \cellcolor[HTML]{FFDDDD}8 & \cellcolor[HTML]{DDFFDD}32 & \cellcolor[HTML]{9B9B9B} \\ \hline
\end{tabular}
\caption{Pairwise comparison matrix used in the Schulze Mehtod. For example, 17 ballots prefer $A>B$ and 33 ballots prefer $B>A$.}
\label{Pairwise comparison matrix}
\end{table}
\subsubsection{Justification}
The Shulze Method is used by multiple organisations around the world. It has been used by various software organisations such as The Wikimedia Foundation, The Debian Project and Ubuntu. It is also used by political parties such as the Pirate Party in Sweden and various other countries. The process also differs greatly in both method and implementation from the two other voting methods used in this paper.
\subsubsection{Pseudocode}
\label{Schulze psuedocode}
let $d[i,j]$ be the number of ballots that prefer candidate $i$ to candidate $j$\\
let $p[i,j]$ be the strength of the strongest path from candidate $i$ to candidate $j$\\
for $i$ from 1 to $C$\\
\tab for $j$ form 1 to $C$\\
\tab\tab if ($i \ne j$)\\
\tab\tab\tab if ($d[i,j] > d[j,i]$)\\
\tab\tab\tab\tab $p[i,j] \coloneqq d[i,j]$\\
\tab\tab\tab else\\
\tab\tab\tab\tab $p[i,j] \coloneqq 0$\\
\tab\tab\tab endif \\
\tab\tab endif \\
\tab endfor \\
endfor\\
for $i$ from 1 to $C$\\
\tab for $j$ form 1 to $C$\\
\tab\tab if ($i \ne j$)\\
\tab\tab\tab for $k$ from 1 to $C$\\
\tab\tab\tab\tab if ($i \ne k \text{ and } j \ne k$)\\
\tab\tab\tab\tab\tab $p[j,k] \coloneqq \text{max }(p[j,k], \text{ min }(p[j,k], p[i,k]))$\\
\tab\tab\tab\tab endif \\
\tab\tab\tab endfor \\
\tab\tab endif \\
\tab endfor \\
endfor\\
\subsubsection{Implementation}
The Shulze Method is implemented within the file \Code{schulze/index.ts}. It takes two inputs: a list of ballots and the number of seats to be elected. A ballot is an ordered list of candidates. The output of the program is a list of winners. The program first creates the matrices for both the prefrences and paths between candidates.
\codeblock{code/schulze/maps.ts}{code:schulze maps}{Data representation}
The program then runs the algorithm outlined in the psuedocode in section \ref{Schulze psuedocode}.
\codeblock{code/schulze/algorithm.ts}{code:schulze algorithm}{Main algorithm}
\section{Evaluation of methods}
\subsection{Sample I}
\subsection{Sample II}
\subsection{Sample III}

\section{Conclusion}

@@

\begin{figure}
	\centering
	\begin{tikzpicture}
		\begin{axis}[
			ybar,
			width = 0.9\textwidth,
			height = 0.5\textwidth,
			legend style={at={(0.5,-0.25)},
			anchor=north,legend columns=-1},
      x tick style = transparent,
			ylabel = {Elections won},
			xlabel = {Candidate},
			ymajorgrids = true,
			every axis plot/.append style={draw=none,fill,no markers},
      ymin = 0,
			symbolic x coords={0,1,2,3,4,5,6,7,8},
			bar width=0.25cm
      ]
			\addplot coordinates
{(0, 563)(1, 337)(2, 100)(3, 0)(4, 0)(5, 0)(6, 0)(7, 0)};
\addplot coordinates
{(0, 323)(1, 203)(2, 474)(3, 0)(4, 0)(5, 0)(6, 0)(7, 0)};
\addplot coordinates
{(0, 333)(1, 255)(2, 412)(3, 0)(4, 0)(5, 0)(6, 0)(7, 0)};

			\legend{FPTP, STV, Schulze}
		\end{axis}
	\end{tikzpicture}
\end{figure}

\begin{figure}
	\centering
	\begin{tikzpicture}
		\begin{axis}[
			ybar,
			width = 0.9\textwidth,
			height = 0.5\textwidth,
			legend style={at={(0.5,-0.25)},
			anchor=north,legend columns=-1},
      x tick style = transparent,
			ylabel = {First prefrence votes},
			xlabel = {Candidate},
			ymajorgrids = true,
			every axis plot/.append style={fill,draw=none,no markers},
      ymin = 0
      ]
			\addplot coordinates
			{(0, 17)(1, 36)(2, 32)(4, 9)(5, 5)(6, 1)};
		\end{axis}
	\end{tikzpicture}
\end{figure}

>>>>

\hypersetup{
	colorlinks,
	citecolor=black,
	filecolor=black,
	linkcolor=black,
	urlcolor=black
}

\usepackage[backend=biber,style=authoryear]{biblatex}
\usepackage[newfloat]{minted}
\usemintedstyle{vs}
\usepackage{csquotes}
\usepackage{caption}
\usepackage{booktabs}

@@

@@

\begin{titlepage}
	\centering
	\vspace{2cm}
	{\Huge Analysis of voting systems: title here\par}
	\vspace{0.6cm}
	{\LARGE Adrian Salamon\par}
	\vspace{0.6cm}
	{\Large Kungsholmens gymnasium\par}
	\vspace{0.4cm}
	{\large Senior thesis\par}
	\vspace{0.6cm}
	\includegraphics[width=0.3\textwidth]{kg}\par\vspace{1cm}
	\vspace{4cm}
	\vfill
	Supervised by: \par
	Maja Kankaanranta

@@

\codeblock{code/typescriptexample.ts}{lst:typescript example}{Basic Typescript syntax}

@@

In order to test the methods and their implementations, test data is needed. There are cases where extensive election data is published, such as in maltese elections, but full ballot data, which is needed for the implementations has not been found. Instead, the implementations will be tested with data generated from a simple computer algorithm. The algorithm used in this paper is highly primitive, as modeling prefrences within a population is far beyond this paper. The full ballot generation program can be found in the \Code{/generator/} folder. The goal of the program is to produce ballots that rank every candidate in order of prefrence (see figure \ref{fig:stv ballot} on page \pageref{fig:stv ballot}). The program represents each voter in a population as belonging to a certain ideology. Each ideology has has a list of weighted prefrences indicating how a voter for this ideology is likely to vote. The weighed prefrences are generated via an abstraction. A single config object is used to create all ideologies.
\codeblock{code/generator/ideologyConfig.ts}{lst:ideology config}{Configuration object for creating ideologies}

@@

The scenario is built around electing one candidate out of eight. The spread of votes within ideologies is flat and all ideologies are "weak". This means that the general spread of votes will be even. An example of the distrubution of first-prefrence votes generated in this scenario can be seen in figure \ref{fig:example of scenario 1}. The full configuration object can be seen in code example \ref{lst:scenario 1}.
\codeblock{code/generator/scenario1.ts}{lst:scenario 1}{Configuration object for scenario 1}
	\caption{Example distrubution of first-prefrence votes in scenario 1}
	\begin{tikzpicture}
		\begin{axis}[
			ybar stacked,
			width = 0.9\textwidth,
			height = 0.5\textwidth,
			legend style={at={(0.5,-0.25)},
			anchor=north,legend columns=-1},
      x tick style = transparent,
			ylabel = {First prefrence votes},
			xlabel = {Candidate},
			ymajorgrids = true,
      ymin = 0,
			yticklabel={\pgfmathprintnumber\tick\%}
      ]
			\addplot coordinates
			{(0, 20)(1, 0)(2, 0)(3, 9)(4, 0)(5, 0)(6, 0)(7, 0)};
			\addplot coordinates
			{(0, 0)(1, 19)(2, 0)(3, 0)(4, 8)(5, 0)(6, 0)(7, 0)};
			\addplot coordinates
			{(0, 0)(1, 0)(2, 22)(3, 0)(4, 0)(5, 12)(6, 6)(7, 4)};
			\legend{Ideology 1, Ideology 2, Ideology 3}
		\end{axis}
	\end{tikzpicture}
	\label{fig:example of scenario 1}
\subsubsection{Scenario 2}
The second scenario elects 3 candidates out of 9 total. It features a normal spread of votes between candidates. An example distribution of first-prefrence votes generated in this scenario can be seen in figure \ref{fig:example of scenario 2}. The full configuration can be seen in code example \ref{lst:scenario 2}.
\codeblock{code/generator/scenario2.ts}{lst:scenario 2}{Scenario 2}
	\caption{Example distrubution of first-prefrence votes in scenario 2}
	\begin{tikzpicture}
		\begin{axis}[
			ybar stacked,
			width = 0.9\textwidth,
			height = 0.5\textwidth,
			legend style={at={(0.5,-0.25)},
			anchor=north,legend columns=-1},
      x tick style = transparent,
			ylabel = {First prefrence votes},
			xlabel = {Candidate},
			ymajorgrids = true,
      ymin = 0,
			yticklabel={\pgfmathprintnumber\tick\%}
      ]
			\addplot coordinates
			{(0, 16)(1, 0)(2, 0)(3, 4)(4, 0)(5, 0)(6, 0)(7, 0)(8, 0)};
			\addplot coordinates
			{(0, 0)(1, 12)(2, 0)(3, 0)(4, 10)(5, 0)(6, 8)(7, 0)(8, 0)};
			\addplot coordinates
			{(0, 0)(1, 0)(2, 22)(3, 0)(4, 0)(5, 13)(6, 0)(7, 9)(8, 6)};
			\legend{Ideology 1, Ideology 2, Ideology 3}
		\end{axis}
	\end{tikzpicture}
	\label{fig:example of scenario 2}
\subsubsection{Scenario 3}
The second scenario elects 3 candidates out of 9 total. It features a steep spread of votes between candidates. An example distribution of first-prefrence votes generated in this scenario can be seen in figure \ref{fig:example of scenario 3}. The full configuration can be seen in code example \ref{lst:scenario 3}.
\codeblock{code/generator/scenario3.ts}{lst:scenario 3}{Scenario 3}
	\caption{Example distrubution of first-prefrence votes in scenario 3}
	\begin{tikzpicture}
		\begin{axis}[
			ybar stacked,
			width = 0.9\textwidth,
			height = 0.5\textwidth,
			legend style={at={(0.5,-0.25)},
			anchor=north,legend columns=-1},
      x tick style = transparent,
			ylabel = {First prefrence votes},
			xlabel = {Candidate},
			ymajorgrids = true,
      ymin = 0,
			yticklabel={\pgfmathprintnumber\tick\%}
      ]
			\addplot coordinates
			{(0, 17)(1, 0)(2, 0)(3, 1)(4, 0)(5, 0)(6, 0)(7, 0)(8, 0)};
			\addplot coordinates
			{(0, 0)(1, 25)(2, 0)(3, 0)(4, 4)(5, 0)(6, 1)(7, 0)(8, 0)};
			\addplot coordinates
			{(0, 0)(1, 0)(2, 40)(3, 0)(4, 0)(5, 10)(6, 0)(7, 2)(8, 0)};
			\legend{Ideology 1, Ideology 2, Ideology 3}
		\end{axis}
	\end{tikzpicture}
	\label{fig:example of scenario 3}

@@

\codeblock{code/fptp/inputs.ts}{lst:fptp inputs}{Inputs for FPTP program}

@@

\codeblock{code/fptp/processing.ts}{lst:fptp processing}{Processing and formatting of data}

@@

\codeblock{code/fptp/result.ts}{lst:fptp result calculation}{Finding and returning winning candidates}

@@

	\label{fig:stv ballot}

@@

\label{alg:stv psuedocode}

@@

The single transferable vote algorithm uses a tree structure to represent the state of the election. Every candidate is a top-level node with an attribute showing the number of current votes for the candidate. Each node has child nodes representing the next prefrences of the voters for that particular candidate, see figure \ref{fig:tree structure}. It is easy to manipulate branches via recursion. Merging and multiplying branches is used when transfering votes from one candidate node to another. A candidate node is a Typescript class. It can be found in the \Code{stv/candidate.ts} file and has the following properties and functions:

@@

	\label{fig:tree structure}

@@

\codeblock{code/stv/candidateNode.ts}{lst:stv candidate node}{The CandidateNode class}

@@

\codeblock{code/stv/distribute.ts}{lst:stv distribute function}{The distribute function}
In order to eliminate and transfer surplus votes from any candidate node $A$, the children of $A$ are passed into the distribute function. In the case of transfering surplus votes, the votes for each child node is first multiplied by $\frac{\text{surplus votes}}{\text{total votes}}$ as outlined in the psuedocode in section \ref{alg:stv psuedocode}. The full source code for funcions that manipulate the tree structure can be found in \Code{/stv/tree.ts}.

The main procces of the program is found in the \Code{stv/election.ts} file and runs the process defined in the psuedocode in section \ref{alg:stv psuedocode} on page \pageref{alg:stv psuedocode}.

\subsection{Schulze}
\subsubsection{Description}
The Schulze Method is a method used mainly to determine results in a single-winner election but can also be used to provide rankings and elect multiple candidates in a single election. Ballots are identical to those of the single transferable vote, see figure \ref{fig:stv ballot} on page \pageref{fig:stv ballot}. The method is compliant with the Condorcet Criterion, which means that if there is a candidate who the majority prefers in a pairwise comparison with every other candidate, that candidate wins. As mentioned, this method relies on comparing the prefrences of every candidate to one another as shown in table \ref{tab:pairwise comparison matrix}. If there is a condorcet winner the process is simple: declare the condorcet winner a winner and run another iteration without that candidate. Repeat this process until all seats are filled. However, there can be condorcet ties, where there is no condorcet winner. There are multiple ways of resolving the tie, one of them being the Schulze Method.

@@

The difficult problem in this method is finding the strongest path between candidates. The problem is called the widest path problem in graph theory. An efficent and relatively simple way to compute this problem is via the Floyd-Warshall algorithm which is used in the implementation. See \ref{lst:schulze algorithm} for the full algorithm.

\begin{table}[H]
\begin{tabular}{l|c|c|c|c|c|}
\cline{2-6}
 & \multicolumn{1}{l|}{A} & \multicolumn{1}{l|}{B} & \multicolumn{1}{l|}{C} & \multicolumn{1}{l|}{D} & \multicolumn{1}{l|}{E} \\ \hline
\multicolumn{1}{|l|}{A} & \cellcolor[HTML]{9B9B9B} & \cellcolor[HTML]{FFDDDD}17 & \cellcolor[HTML]{FFDDDD}14 & \cellcolor[HTML]{DDFFDD}35 & \cellcolor[HTML]{DDFFDD}30 \\ \hline
\multicolumn{1}{|l|}{B} & \cellcolor[HTML]{DDFFDD}33 & \cellcolor[HTML]{9B9B9B} & \cellcolor[HTML]{FFDDDD}24 & \cellcolor[HTML]{DDFFDD}47 & \cellcolor[HTML]{DDFFDD}36 \\ \hline
\multicolumn{1}{|l|}{C} & \cellcolor[HTML]{DDFFDD}36 & \cellcolor[HTML]{DDFFDD}26 & \cellcolor[HTML]{9B9B9B} & \cellcolor[HTML]{DDFFDD}40 & \cellcolor[HTML]{DDFFDD}42 \\ \hline
\multicolumn{1}{|l|}{D} & \cellcolor[HTML]{FFDDDD}15 & \cellcolor[HTML]{FFDDDD}3 & \cellcolor[HTML]{FFDDDD}10 & \cellcolor[HTML]{9B9B9B} & \cellcolor[HTML]{FFDDDD}18 \\ \hline
\multicolumn{1}{|l|}{E} & \cellcolor[HTML]{FFDDDD}20 & \cellcolor[HTML]{FFDDDD}14 & \cellcolor[HTML]{FFDDDD}8 & \cellcolor[HTML]{DDFFDD}32 & \cellcolor[HTML]{9B9B9B} \\ \hline
\end{tabular}
\caption{Pairwise comparison matrix used in the Schulze Mehtod. For example, 17 ballots prefer $A>B$ and 33 ballots prefer $B>A$.}
\label{tab:pairwise comparison matrix}
\end{table}
The Shulze Method is used by multiple organisations around the world. It has been used by various software organisations such as The Wikimedia Foundation, The Debian Project and Ubuntu. It is also used by political parties such as the Pirate Party in Sweden and various other countries. The process also differs greatly in both method and implementation from the two other voting methods used in this paper.
\label{alg:schulze psuedocode}
let $d[i,j]$ be the number of ballots that prefer candidate $i$ to candidate $j$\\
let $p[i,j]$ be the strength of the strongest path from candidate $i$ to candidate $j$\\
for $i$ from 1 to $C$\\
\tab for $j$ form 1 to $C$\\
\tab\tab if ($i \ne j$)\\
\tab\tab\tab if ($d[i,j] > d[j,i]$)\\
\tab\tab\tab\tab $p[i,j] \coloneqq d[i,j]$\\
\tab\tab\tab else\\
\tab\tab\tab\tab $p[i,j] \coloneqq 0$\\
\tab\tab\tab endif \\
\tab\tab endif \\
\tab endfor \\
endfor\\
for $i$ from 1 to $C$\\
\tab for $j$ form 1 to $C$\\
\tab\tab if ($i \ne j$)\\
\tab\tab\tab for $k$ from 1 to $C$\\
\tab\tab\tab\tab if ($i \ne k \text{ and } j \ne k$)\\
\tab\tab\tab\tab\tab $p[j,k] \coloneqq \text{max }(p[j,k], \text{ min }(p[j,k], p[i,k]))$\\
\tab\tab\tab\tab endif \\
\tab\tab\tab endfor \\
\tab\tab endif \\
\tab endfor \\
endfor\\
The Shulze Method is implemented within the file \Code{schulze/index.ts}. It takes two inputs: a list of ballots and the number of seats to be elected. A ballot is an ordered list of candidates. The output of the program is a list of winners. The program first creates the matrices for both the prefrences and paths between candidates.
\codeblock{code/schulze/maps.ts}{lst:schulze maps}{Data representation}
The program then runs the algorithm outlined in the psuedocode in section \ref{alg:schulze psuedocode}.
\codeblock{code/schulze/algorithm.ts}{lst:schulze algorithm}{Main algorithm}
\section{Evaluation of results}
\subsection{Scenario 1}
Scenario 1 featured 8 candidates where one was to be elected. Vote spread was flat, meaning that votes tend to be diverse in their prefrences. This means that there is not an abvious winner present. This can be seen from the first-prefrence votes in the scenario seen in figure \ref{fig:example of scenario 1}. The full result in this scenario can be seen in figure \ref{fig:scenario 1 results}. The outlier in this scenario seems to be the fptp method, electing candidate 0 more often than both other methods. Key metrics for the results in this scenario can be found in table \ref{tab:scenario 1 result}.
	\begin{tikzpicture}
		\begin{axis}[
			ybar,
			width = 0.9\textwidth,
			height = 0.5\textwidth,
			legend style={at={(0.5,-0.25)},
			anchor=north,legend columns=-1},
      x tick style = transparent,
			ylabel = {Elections won},
			xlabel = {Candidate},
			ymajorgrids = true,
			every axis plot/.append style={draw=none,fill,no markers},
      ymin = 0,
			symbolic x coords={0,1,2,3,4,5,6,7,8},
			bar width=0.25cm
      ]
			\addplot coordinates
			{(0, 273)(1, 59)(2, 668)(3, 0)(4, 0)(5, 0)(6, 0)(7, 0)};
			\addplot coordinates
			{(0, 37)(1, 4)(2, 959)(3, 0)(4, 0)(5, 0)(6, 0)(7, 0)};
			\addplot coordinates
			{(0, 42)(1, 4)(2, 954)(3, 0)(4, 0)(5, 0)(6, 0)(7, 0)};
			\legend{FPTP, STV, Schulze}
		\end{axis}
	\end{tikzpicture}
	\caption{Figure thingy}
	\label{fig:scenario 1 results}

\begin{table}[H]
\centering
\caption{Key metrics for result in scenario 1}
\label{tab:scenario 1 result}
\begin{tabular}{@{}lccc@{}}
\toprule
Method & Standard deviation & Missrepresentation & Most likely winners \\ \midrule
FPTP & 223 & 67\% & 2 \\
STV & 315 & 7\% & 2 \\
Schulze & 313 & 9\% & 2 \\ \bottomrule
\end{tabular}
\end{table}
% [ 223.39259164082, 315.44928276983, 313.6271671906]
\subsection{Scenario 2}
\begin{figure}[H]
	\centering
	\begin{tikzpicture}
		\begin{axis}[
			ybar,
			width = 0.9\textwidth,
			height = 0.5\textwidth,
			legend style={at={(0.5,-0.25)},
			anchor=north,legend columns=-1},
      x tick style = transparent,
			ylabel = {Elections won},
			xlabel = {Candidate},
			ymajorgrids = true,
			every axis plot/.append style={draw=none,fill,no markers},
      ymin = 0,
			symbolic x coords={0,1,2,3,4,5,6,7,8},
			bar width=0.25cm
      ]
			\addplot coordinates
			{(0, 973)(1, 267)(2, 1000)(3, 0)(4, 12)(5, 743)(6, 0)(7, 5)(8, 0)};
			\addplot coordinates
			{(0, 456)(1, 808)(2, 1000)(3, 0)(4, 33)(5, 703)(6, 0)(7, 0)(8, 0)};
			\addplot coordinates
			{(0, 338)(1, 160)(2, 1000)(3, 0)(4, 0)(5, 1000)(6, 0)(7, 502)(8, 0)};
			\legend{FPTP, STV, Schulze}
		\end{axis}
	\end{tikzpicture}
	\caption{Figure thingy numero duo}
	\label{fig:scenario 2 result}
\end{figure}

\begin{table}[H]
\centering
\caption{Key metrics for result in scenario 2}
\label{tab:scenario 2 result}
\begin{tabular}{@{}lccc@{}}
\toprule
Method & Standard deviation & Missrepresentation & Most likely winners \\ \midrule
FPTP & 418 & 42\% & 0, 2 \& 5 \\
STV & 388 & 14\% & 1, 2 \& 5 \\
Schulze & 393 & 67\% & 2, 5 \& 7  \\ \bottomrule
\end{tabular}
\end{table}
% [ 418.13628234977, 388.17206952015, 393.25535950293 ]
\subsection{Scenario 3}
\begin{figure}[H]
	\centering
	\begin{tikzpicture}
		\begin{axis}[
			ybar,
			width = 0.9\textwidth,
			height = 0.5\textwidth,
			legend style={at={(0.5,-0.25)},
			anchor=north,legend columns=-1},
      x tick style = transparent,
			ylabel = {Elections won},
			xlabel = {Candidate},
			ymajorgrids = true,
			every axis plot/.append style={draw=none,fill,no markers},
      ymin = 0,
			symbolic x coords={0,1,2,3,4,5,6,7,8},
			bar width=0.25cm
      ]
			\addplot coordinates
			{(0, 994)(1, 1000)(2, 1000)(3, 0)(4, 0)(5, 6)(6, 0)(7, 0)(8, 0)};
			\addplot coordinates
			{(0, 1000)(1, 1000)(2, 1000)(3, 0)(4, 0)(5, 0)(6, 0)(7, 0)(8, 0)};
			\addplot coordinates
			{(0, 999)(1, 1000)(2, 1000)(3, 0)(4, 0)(5, 1)(6, 0)(7, 0)(8, 0)};
			\legend{FPTP, STV, Schulze}
			\end{axis}
	\end{tikzpicture}
	\caption{Figure thingy tré}
	\label{fig:scenario 3 result}
\end{figure}
\begin{table}[H]
\centering
\caption{Key metrics for result in scenario 3}
\label{tab:scenario 3 result}
\begin{tabular}{@{}lccc@{}}
\toprule
Method & Standard deviation & Missrepresentation & Most likely winners \\ \midrule
FPTP & 470 & 33\% & 0, 1 \& 2 \\
STV & 471 & 33\% & 0, 1 \& 2 \\
Schulze & 471 & 3\% & 0, 1 \& 2  \\ \bottomrule
\end{tabular}
\end{table}

%[ 469.99669029568, 471.40452079103, 471.16899539573 ]
\section{Conclusion}
Proportionalities: 1:67,7,9 2:42,14,67, 3:33,33,33

@@
